%-------------------------
% Resume in Latex
% Author : Jake
% % License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeEducation}[2]{
  \item\small{
    \textit{\small#1} \hfill \textit{\small#2}
  }
}
% \textit{\small{#1} \hfill \textit{\small{#2}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{4.1pt}
\begin{document}

%-----------HEADER-----------
\begin{center}
    \textbf{\Huge \scshape Umut Toker} \\ \vspace{1pt}
    \texttt Tampa, FL $|$
    \href{mailto:utoker@gmail.com}{\texttt{utoker@gmail.com}} $|$ 
    \href{https://linkedin.com/in/utoker}{\texttt{linkedin.com/in/utoker}} $|$
    \href{https://github.com/utoker}{\texttt{github.com/utoker}} $|$
    \href{https://utoker.com}{\texttt{utoker.com}} 
\end{center}

%-----------SUMMARY-----------
\section*{Profile}
Full-stack developer skilled in React, Next.js, and REST APIs with a track record of delivering high-performance, scalable web apps. 
Proficient in TypeScript, Python and SQL. 
Certified in AWS \& Azure; currently pursuing an M.S. in Software Engineering.

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript/JavaScript, Python, SQL (PostgreSQL, T-SQL), HTML/CSS} \\[3pt]
     \textbf{Frameworks}{: React 19, Next.js 15, Django, Node.js, React Native, Tailwind, Radix, shadcn/ui, Zod } \\ [3pt]
     \textbf{Cloud \& DevOps}{: Supabase, AWS, Azure, DigitalOcean, Vercel, Docker} \\ [3pt]
     \textbf{Tools}{: Git, Linux, VS Code, Resend API} \\ [3pt]
    }}
 \end{itemize}

 %-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://reqq.cc}{reqq.cc}} - {URL shortener} \\
          \small\emph{TypeScript · React 19 · Next.js 15 · Tailwind v4 · Radix · shadcn/ui · Zod · Supabase (PostgreSQL)}}{}
          \resumeItemListStart
            \resumeItem{Achieved 32 ms p95 redirect latency (-91\%) by offloading slug lookup to Vercel Edge Middleware.}
            \resumeItem{Secured 100\% of write operations with Supabase RLS and Zod validations.}
            \resumeItem{Modularized backend logic into Next.js Server Actions, cutting server bundle by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
        \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/utoker/food-check}{Food Check}} - {React Native grocery-scanner } \\
          \small\emph{React Native · Expo SDK · RNE UI · React Navigation · Axios}}{}
          \resumeItemListStart
            \resumeItem{Built camera-based UPC scanner that calls USDA FoodData API and displays nutrition info.  }
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Support Engineer}{Oct 2023 -- Jun 2025}
      {Advanco SA}{Princeton, NJ}
      \resumeItemListStart
      \resumeItem{Automated deployment and configuration via T-SQL scripts, reducing setup time by 2 hrs/client.}
      \resumeItem{Authored T-SQL scripts that resolved 50\% of live-data anomalies within 30 min.}
      \resumeItem{Collaborated with R\&D to debug software, reproduce issues, analyze logs, and deliver coordinated hotfixes.}
      \resumeItem{Wrote and maintained install/debug guides, training 2 teammates improving first-line resolution rates by 35\%.}
      \resumeItem{Led onsite client-facing installation and validation for Thermo Fisher Scientific site in Italy.}
      \resumeItem{Stakeholder communication: Demoed ARC platform to 200+ industry attendees at HDA2024, collecting feedback that informed two UI fixes.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Associate Software Engineer (Volunteer)}{Feb 2023 -- Jun 2023}
      {The City Tutors}{NYC, NY}
      \resumeItemListStart
        \resumeItem{Six-month pro-bono sprint to modernize authentication and reduce help-desk load.}
        \resumeItem{Engineered a Username recovery system using Python and Django, reducing support tickets by 30\%.}
        \resumeItem{Improved successful login rates by 22\% by redesigning the login page using Django and custom validation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

 %-----------EDUCATION-----------
\section{Education}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
{M.S. Software Engineering - Western Governors University}\hfill \textit{UT, 2025 - 2027 (exp.)} \\[3pt]
{B.B.A. - Eskisehir Osmangazi University} \hfill \textit{Turkey, 2014 - 2019} \\[3pt]
  }}
  \end{itemize}

  %-----------CERTIFICATIONS-----------------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    {AWS Certified Cloud Practitioner} - ID: 3LPFBSV1XER4Q7KS \\[3pt]
    {Azure Fundamentals} - ID: c7864b78cd5dc87b \\[3pt]
    {Introduction to Python Programming} - Western Governors University \\[3pt]
    {Scientific Computing with Python} - 300 hours \\[3pt]
    {JavaScript Algorithms and Data Structures} - 300 hours \\[3pt]
      }}
  \end{itemize}

%-------------------------------------------
\end{document}
